\textbf{Real-time guitar transcription using\\Fourier transform based methods}\\A pitch estimation framework and overtone sieve algorithm

### 2021-04-15 paper.tex
table text

    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_2$.}

>>>>

    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_2$. Given an $n$ semitone interval, we list if we find both notes and if not, if one of the notes was found an octave higher. We also list the other reported notes.}
